---
title: "hw5"
author: "Nathan De Los Santos"
output:
  pdf_document: default
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidymodels)
library(tidyverse)
library(ISLR) # For the Smarket data set
library(ISLR2) # For the Bikeshare data set
library(discrim)
library(poissonreg)
library(corrr)
library(klaR) # for naive bayes
library(ggplot2)
library(ggthemes)
library(pROC)
tidymodels_prefer()
pokemon_data <- read.csv('homework-5/data/pokemon.csv')
```

## Question 1

```{r}
library(janitor)

pokemon <- clean_names(pokemon_data)
```
The clean_names() function is useful because it removes spaces from variable names and can also alter the capitalization depending on what you specify. Moreover, all variable names are unique and can only consist of characters, numbers, and letters.

## Question 2

```{r}
pokemon %>%
  ggplot(aes(y = type_1)) +
  geom_bar()
```
There are 18 classes for Pokemon types. By looking at the graph, we can see that "flying" types are relatively low in count.

```{r}
pokemon %>%
  filter(type_1 == c('Bug', 'Fire', 'Grass', 'Normal', 'Water', 'Psychic'))

pokemon$type_1 <- factor(pokemon$type_1)
pokemon$legendary <- factor(pokemon$legendary)
```

## Question 3

```{r}
pokeSplit <- initial_split(pokemon, prop = 0.7, strata = type_1)
pokeTrain <- training(pokeSplit)
pokeTest <- testing(pokeSplit)
```
Total Observations: 800
Training: 559 (800*.7)
Testing: 241 (800*.3)

```{r}
pokeFold <- vfold_cv(pokeTrain, strata = type_1, v = 5)
```
Stratifying on a k-fold cross validation is beneficial because it ensures that each fold is an appropriate representative of the whole data set.

## Question 4

```{r}
pokeRecipe <- recipe(type_1 ~ legendary + generation + sp_atk + attack, speed, defense, hp, sp_def, data=pokeTrain) %>% 
  step_dummy(all_nominal_predictors()) %>%
  step_center(all_nominal_predictors()) %>% 
  step_scale(all_nominal_predictors())
```

## Question 5

```{r}
pokeFit <- multinom_reg(penalty = tune(), mixture = tune()) %>% 
  set_engine('glmnet') %>% 
  set_mode('classification')

pokeFlow <- workflow() %>% 
  add_model(pokeFit) %>% 
  add_recipe(pokeRecipe)

pokeGrid <- grid_regular(penalty(range = c(-5, 5)), mixture(range = c(0, 1)), levels = 10)
```
In total, we will be fitting 500 models when we fit the models to the folded data.

## Question 6

```{r}
pokeTune <- tune_grid(pokeFlow, resamples = pokeFold, grid = pokeGrid)
```

## Question 7

```{r}
pokeBest <- select_best(pokeTune, metric = 'roc_auc')

pokeFinal <- finalize_workflow(pokeFlow, pokeBest)

pokeLast <- fit(pokeFinal, data = pokeTrain)

pokePredict <- augment(pokeLast, new_data = pokeTest) %>% 
  select(type_1, starts_with(".pred"))
```

## Question 8

```{r}
pokePredict %>% roc_auc(type_1, .pred_Bug:.pred_Water)
```
